Pillar 2 - Topic Modeling

### 2019-03-20 Pillar 2 - Topic Modeling.Rmd
starting to clean lda fit test

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

@@

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

@@

save(result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

save(result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

save(result_manual, result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

The following functions allow us to inspect the distributions and get kw
```{r}
# FUNCTION
#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}

# get_top_match <- function(d_distribution){
#   print(!!sym(d_distribution))
# }

@@

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

>>>>

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control_fast,
  mc.cores = 4L

@@

```{r package test on topics, cache = TRUE}
start.time <- Sys.time()

result_topic_test <- map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 15, by = 5))

@@

#save(result_topic_test,
#     file = "Output/LDA_ntopics.RDATA")

@@

save(result_overview ,
     file = "Output/LDA_ntopics.RDATA")

@@

save(result_manual, result_overview ,
     file = "Output/LDA_ntopics.RDATA")

@@

The following functions allow us to inspect the distributions and get kw
```{r}
# FUNCTION
# #get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
# 
#  get_top_match <- function(d_distribution){
#    
#   #save user input as string
#   name_selected <- deparse(substitute(d_distribution))
#   beta_gamma_sym <- tolower(name_selected)
#   
#   #prepare variables for grouping
#   grouping <- ifelse(name_selected == "Beta", "topic", "document")
#   top_num <- ifelse(name_selected  == "Beta", 10, 5) #select how many terms or topics(respectively) to show
#   
#  }

@@

##Plots - Model Evaluation
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){
